The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-10-11 rnw/Twophase_Estimators and their Application.Rnw
update Andreas 11.10.2017(3)

The \textit{g-weight} formulation is
\begin{subequations}\label{eq:gw_var_2p_reg}
\begin{align}
  \hat{\var}(\hat{Y}_{reg2p,ex}) & :=\bar{\pmb{Z}}^t\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}\bar{\pmb{Z}} \label{eq:gw_var_2p_reg_ex}\\
  \hat{\var}(\hat{Y}_{reg2p,nex}) & :=
  \hat{\bar{\pmb{Z}}}^t\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}\hat{\bar{\pmb{Z}}}
  + \hat{\pmb{\beta}}_{s_2}^t\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{1}}\hat{\pmb{\beta}}_{s_2} \label{eq:gw_var_2p_reg_nex}
\end{align}
\end{subequations}

where the g-weight variance-covariance matrix of $\hat{\beta}_{s_2}$ is calculated as

@@

Note that when applied to internal linear regression models, the external variance is asymptotically unbiased and usually slightly smaller than the g-weight variance, where the uncertainty of the regression coefficients is accounted for by the variance-covariance matrix (Eq. \ref{eq:estvarmatrix}).  The external variances are provided in the package \pkg{forestinventory} in case the user wants to compare linear models to another model type where no g-weight formation is possible, as is the case with non-parametric models like kNN.

@@

The \textbf{exhaustive} case requires a closer look. Since being in the infinite population approach, $\pmb{Z}(x)$ again refers to the sample point $x$ and not the area around it. Deriving the \textit{exact} spatial mean, $\bar{\pmb{Z}}=\frac{1}{\lambda(F)}\int_{x \in F} \pmb{Z}(x)dx= (\frac{1}{\lambda(F)}\int_{x \in F} z_1(x)dx, ..., \frac{1}{\lambda(F)}\int_{x \in F} z_p(x)dx)^t$, implies that we need to calculate the spatial means of each component of $\pmb{Z}(x)$ using all possible points in $F$. This is much like the situation we had with calculating the mean of the local density surface for $Y(x)$ in that we need to find the mean of $\pmb{Z}(x)$ over an infinite number of sample points (i.e. $n_1=\infty$). Of course this is practically infeasible, but there are few cases where the exact mean can also be precisely calculated in the infinite population framework. The first case is when the explanatory variables are provided by polygon layers (e.g. map of development stages). In this case, one can calculate the exact mean as the area-weighted average of each categorical variable. The second case is when the exact mean can be calculated in one step, e.g. taking the mean of all height pixels of a raster canopy height model will perfectly equal the mean calculated by the use of an infinite number of supports \citep{mandallaz2013b}. In all other cases, one can only try to get a reasonable approximation of $\bar{\pmb{Z}}$.\par

One possibility to approximate the exact mean $\bar{\pmb{Z}}$ is shown in Fig. \ref{fig:exh_nexh_and_boundweights_a}, which illustrates the implemented solution to the exhaustive use of the auxiliary information described in \citet{mandallaz2013b}. In order for all of the wall-to-wall auxiliary information to be exploited, the spatial arrangement of the supports were tesselated to form a perfect partition over the inventory area as is the case with the dark green polygons (squares tiles in this case). Is has to be noted that this would perfectly enable for calculating the exact mean $\bar{\pmb{Z}}$ in the \textit{finite} population approach, i.e. deriving $\pmb{Z}(x)$ for the entire finite population of supports and consequently calculating the exact mean $\bar{\pmb{Z}}$. While this is not equal to the exact mean $\bar{\pmb{Z}}$ in the infinite population approach, $n_1$ is still expected to be reasonably large to assume a good approximation of $\bar{\pmb{Z}}$ as long as the size of the supports are not unreasonably large. Whereas this implementation provides a convenient flexibility to switch between extimators of both the finite and infinite approach using the \textit{same} data set, it can also impose practical drawbacks. One is that a perfect tesselation by the supports strongly depends on the distance between the sample locations of $s_1$ in combination with the spatial extent of the support. Since in practice the support size will rather be chosen in order to achieve a best possible explanatory power of the regression model, thus minimizing the residual variation, a perfect tesselation might not always be feasible. In the infinite population frame however, the supports are also allowed to overlap if this seems necessary to acquire a sufficiently large sample $n_1$ of $\pmb{Z}(x)$ to get a reasonable approximation of $\bar{\pmb{Z}}$. This is again because $\pmb{Z}(x)$ only refers to the sample point and has no spatial association. With this respect, the infinite population approach can thus provide more flexibility than the finite approach. One could even consider the use of different support sizes per explanatory variable as long as they are consistently used at all sample locations.

@@

An extension to the so-far published estimators by Mandallaz is the consideration of a \textit{\textbf{boundary adjustment}}. In forest inventories, the sample is often restricted to those sample locations located within the forest area. In case a consistent forest definition can be applied to both the $s_2$ and $s_1$ sample (e.g. by a polygon forest mask layer), it might be desired to restrict the calculation of the explanatory variables to the forest area within the given support (see Fig. \ref{fig:exh_nexh_bw}). This method was suggested in \citet{mandallaz2013b} and led to an improvement in estimation precision. In order to ensure an unbiased calculation of either $\hat{\bar{\pmb{Z}}}$ or $\bar{\pmb{Z}}$, the respective means have then to be calculated as the \textit{weighted} mean where the weight $w(x)$ is equal to the percentage of forested area within the support of sample location $x$.

@@

To demonstrate the use of the global two-phase estimators, we will use the \code{grisons} data set that comes with installing the package from the CRAN repository. The dataset contains data from a simple (i.e. non-cluster) two-phase forest inventory conducted in 2007 that was used in \citet{mandallaz2013b} as a case study. The $s_1$ sample is comprised of 306 sample locations arranged on a systematic grid containing auxiliary information in the form of LiDAR canopy height metrics (\code{mean}, \code{stddev}, \code{max}, \code{q75}). Auxiliary information for all 306 plots is provided in the form of LiDAR canopy height metrics (\code{mean}, \code{stddev}, \code{max}, \code{q75}). For a systematic subsample of 67 ($s_2$ sample), terrestrial information of the timber volume per hectare (\code{tvol}) on the sample plot level is provided from a terrestrial survey. We can load \pkg{forestinventory} and examine the \code{grisons} data set in the \proglang{R} environment as follows:

@@

The \textbf{exhaustive estimator} can be applied by additionally passing a vector containing the \textit{exact} means of the explanatory variables, i.e. $\bar{\pmb{Z}}$, to the optional argument \code{exhaustive}. This vector must be calculated beforehand in such a way that any desired boundary adjustment has already been applied. Note that the vector input to \code{exhaustive} must be in the same order that the \code{lm()}-function processes a \code{formula} object including the intercept term whose exact mean will always be 1. Particular caution must be taken if categorical variables are present because the \code{lm()}-function, which is internally used to set up the design-matrix, automatically creates dummy variables with one of the categories used as a reference. The correct order for our \code{grisons} example can easily be extracted using:

@@

In the equations for the point estimates (Eq. \ref{eq:pointest_2p_small} and \ref{eq:pepsmall}), we see that the globally derived regression coefficients are applied to the exhaustively or non-exhaustively calculated means of the explanatory variables ($\bar{\pmb{Z}}_G$, $\hat{\bar{\pmb{Z}}}_G$) which are now only based on the first-phase sample $s_{1,G}$ located within small area $G$. A potential bias of the regression model predictions in the small area $G$, due to fitting the regression model with data outside of $G$, is then corrected by adding the mean of the empirical model residuals in $G$. This is called the \textit{bias} or \textit{residual correction} term.

@@

where the variance-covariance matrix of the auxiliary vector $\hat{\bar{\pmb{Z}}}_G$ is estimated by
\begin{equation}\label{estvarcovaux_G}
\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{G}}=
\frac{1}{n_{G}(n_{G}-1)}\sum_{x\in{s_{1,G}}}
(\pmb{Z}(x)-\hat{\bar{\pmb{Z}}}_{G})(\pmb{Z}(x)-\hat{\bar{\pmb{Z}}}_{G})^t
\end{equation}

@@

\begin{subequations}\label{eq:pest_2p_extsynth_extpsynth}
\begin{align}
\hat{Y}_{G,extsynth,2p} & = \bar{\pmb{\mathbb{Z}}}^t_{G}\hat{\pmb{\theta}}_{s_2} \label{eq:pointest_2p_extsynth} \\
\hat{Y}_{G,extpsynth,2p} & =\hat{\bar{\pmb{\mathbb{Z}}}}_{G}^t\hat{\pmb{\theta}}_{s_2} \label{eq:pointest_2p_extsynth} \\
\hat{\var}(\hat{Y}_{G,extsynth,2p}) & = \bar{\pmb{\mathbb{Z}}}^t_{G}\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{s_2}}\bar{\pmb{\mathbb{Z}}}_{G} \label{eq:var_2p_extsynth} \\
\hat{\var}(\hat{Y}_{G,extpsynth,2p})& =
\hat{\bar{\pmb{\mathbb{Z}}}}_{G}^t\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{s_2}}
\hat{\bar{\pmb{\mathbb{Z}}}}_{G}
+ \hat{\pmb{\theta}}^t_{s_2}\hat{\Sigma}_{\hat{\bar{\pmb{\mathbb{Z}}}}_{1,G}}\hat{\pmb{\theta}}_{s_2} \label{eq:var_2p_extpsynth}
\end{align}
\end{subequations}

@@

\begin{subequations}\label{eq:ext_varexternal_2p_extsynth}
\begin{align}
  \hat{\var}_{ext}(\hat{Y}_{G,extsynth,2p}) & = \frac{1}{n_{2,G}}\hat{\var}_{s_{2,G}}(\hat{\mathbb{R}}(x)) \label{eq:ext_varexternal_2p_extsynth} \\
  \hat{\var}_{ext}(\hat{Y}_{G,extpsynth,2p}) & = \frac{1}{n_{1,G}}\hat{\var}_{s_{2,G}}(Y(x)) + \Big(1-\frac{n_{2,G}}{n_{1,G}}\Big)\frac{1}{n_{2,G}}\hat{\var}_{s_{2_G}}(\hat{\mathbb{R}}(x)) \label{eq:ext_varexternal_2p_extpsynth}
\end{align}
\end{subequations}
where $\hat{\mathbb{R}}(x)=Y(x)-\bar{\pmb{\mathbb{Z}}}^t_{G}\hat{\pmb{\theta}}_{s_2}$.

To summarize, the (pseudo) synthetic estimator can be applied whether terrestrial inventory sample is found in the small area or not, but has a deceptively small g-weight variance due to its potential bias.  When terrestrial sample is observed in the small area, we can produce (asymptotically) design-unbiased estimates and variances using either \textit{small} or \textit{psmall} which remove this bias directly with a mean residual term, or more elegantly with \textit{extsynth} or \textit{extpsynth} which simply uses the same synthetic formulas while including an indicator variable for the small area in the model formula to remove the bias by construction in OLS.

@@

The \pkg{forestinventory} package automatically includes the indicator variable for the small area behind the scenes so there is no need for the user to implement it. Notice that the $R^2$s (\code{r.squared}) under the \textit{extpsynth} estimator vary between small areas, while they are identical under the \textit{psmall} estimator. This is because under the \textit{extpsynth} estimator, the regression model is recalculated for each small area estimation after adding the indicator variable for the respective small area in the globally derived design matrices. In case of the  \textit{psmall} estimator, the regression model stays the same for each small area estimation. Although the results of both estimators should always be close to each other, we recommend applying both estimators and compare the results afterwards in order to reveal unsuspected patterns in the data, particularly in the case of cluster sampling (see Section \ref{sec:speccas_and_scen}).\par

@@

The \textbf{exhaustive versions} of the small area estimators (Eq. \ref{eq:pointest_2p_small},\ref{eq:var_2p_reg_small},\ref{eq:varext_2p_reg_small},\ref{eq:pointest_2p_reg_synth},\ref{eq:var_2p_reg_synth}) are specified via the optional argument \code{exhaustive}. Its application requires that we know the exact means of all explanatory variables within the small area(s) of interest. In contrast to the \textit{global} estimators, the exact means have now to be delivered in the form of a \code{data.frame}, where each row corresponds to a small area, and each column specifies the exact mean of the respective explanatory variable. Note that likewise the case of global estimation, the order of the explanatory variables in the data frame has to match the order in which they appear in the design matrix defined by the \code{lm()}-function in \proglang{R}. In order to tell \proglang{R} which row describes which small area, the row names have to match the respective names of the small areas specified in the \code{areas} argument.

>>>>

The \textit{g-weight} formulation is
\begin{subequations}\label{eq:gw_var_2p_reg}
\begin{align}
  \hat{\var}(\hat{Y}_{reg2p,ex}) & :=\bar{\pmb{Z}}^t\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}\bar{\pmb{Z}} \label{eq:gw_var_2p_reg_ex}\\
  \hat{\var}(\hat{Y}_{reg2p,nex}) & :=
  \hat{\bar{\pmb{Z}}}^t\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}\hat{\bar{\pmb{Z}}}
  + \hat{\pmb{\beta}}_{s_2}^t\hat{\pmb{\Sigma}}_{\hat{\bar{\pmb{Z}}}}\hat{\pmb{\beta}}_{s_2} \label{eq:gw_var_2p_reg_nex}
\end{align}
\end{subequations}

where the g-weight variance-covariance matrix of $\hat{\pmb{\beta}}_{s_2}$ is calculated as

@@

Note that when applied to internal linear regression models, the external variance is asymptotically unbiased and usually slightly smaller than the g-weight variance, where the uncertainty of the regression coefficients is accounted for by the variance-covariance matrix (Eq. \ref{eq:estvarmatrix}).  The external variances are provided in the package \pkg{forestinventory} in case the user wants to compare linear models to another model type where no g-weight formulation is possible, as is the case with non-parametric models like kNN.

@@

The \textbf{exhaustive} case requires a closer look. Since being in the infinite population approach, $\pmb{Z}(x)$ again refers to the sample point $x$ and not the area around it. Deriving the \textit{exact} spatial mean, $\bar{\pmb{Z}}=\frac{1}{\lambda(F)}\int_{F} \pmb{Z}(x)dx= (\frac{1}{\lambda(F)}\int_{F} z_1(x)dx, ..., \frac{1}{\lambda(F)}\int_{F} z_p(x)dx)^t$, implies that we need to calculate the spatial means of each component of $\pmb{Z}(x)$ using all possible points in $F$. This is much like the situation we had with calculating the mean of the local density surface for $Y(x)$ in that we need to find the mean of $\pmb{Z}(x)$ over an infinite number of sample points (i.e. $n_1=\infty$). Of course this is practically infeasible, but there are few cases where the exact mean can also be precisely calculated in the infinite population framework. The first case is when the explanatory variables are provided by polygon layers (e.g. map of development stages). In this case, one can calculate the exact mean as the area-weighted average of each categorical variable. The second case is when the exact mean can be calculated in one step, e.g. taking the mean of all height pixels of a raster canopy height model will perfectly equal the mean calculated by the use of an infinite number of supports \citep{mandallaz2013b}. In all other cases, one can only try to get a reasonable approximation of $\bar{\pmb{Z}}$.\par

One possibility to approximate the exact mean $\bar{\pmb{Z}}$ is shown in Fig. \ref{fig:exh_nexh_and_boundweights_a}, which illustrates the implemented solution to the exhaustive use of the auxiliary information described in \citet{mandallaz2013b}. In order for all of the wall-to-wall auxiliary information to be exploited, the spatial arrangement of the supports were tesselated to form a perfect partition over the inventory area as is the case with the dark green polygons (squares tiles in this case). Is has to be noted that this would perfectly enable for calculating the exact mean $\bar{\pmb{Z}}$ in the \textit{finite} population approach, i.e. deriving $\pmb{Z}(x)$ for the entire finite population of supports and consequently calculating the exact mean $\bar{\pmb{Z}}$. While this is not equal to the exact mean $\bar{\pmb{Z}}$ in the infinite population approach, $n_1$ is still expected to be reasonably large to assume a good approximation of $\bar{\pmb{Z}}$ as long as the size of the supports are not unreasonably large. Whereas this implementation provides a convenient flexibility to switch between extimators of both the finite and infinite approach using the \textit{same} data set, it can also impose practical drawbacks. One is that a perfect tesselation by the supports strongly depends on the distance between the sample locations of $s_1$ in combination with the spatial extent of the support. Since in practice the support size will rather be chosen in order to achieve a best possible explanatory power of the regression model, thus minimizing the residual variation, a perfect tesselation might not always be feasible. In the infinite population frame however, the supports are also allowed to overlap if this seems necessary to acquire a sufficiently large sample $n_1$ of $\pmb{Z}(x)$ to get a reasonable approximation of $\bar{\pmb{Z}}$. This is again because $\pmb{Z}(x)$ only refers to the sample point and has no spatial association. With this respect, the infinite population approach can thus provide more flexibility than the finite approach. One could also consider the use of different support sizes per explanatory variable as long as they are consistently used at all sample locations.

@@

An extension to the so-far published estimators by Mandallaz is the consideration of a \textit{\textbf{boundary adjustment}}. In forest inventories, the sample is often restricted to those sample locations located within the forest area. In case a consistent forest definition can be applied to both the $s_2$ and $s_1$ sample (e.g. by a polygon forest mask layer), it might be desired to restrict the calculation of the explanatory variables to the forest area within the given support (see Fig. \ref{fig:exh_nexh_bw}). This method was suggested in \citet{mandallaz2013b} and led to an improvement in estimation precision. In order to ensure an unbiased calculation of either $\hat{\bar{\pmb{Z}}}$ or $\bar{\pmb{Z}}$, the respective means have then to be calculated as the \textit{weighted} mean (Eq. \ref{eq:wmeanZ}) where the weight $w(x)$ is equal to the percentage of forested area within the support of sample location $x$.

@@

To demonstrate the use of the global two-phase estimators, we will use the \code{grisons} data set that comes with installing the package from the CRAN repository. The data set contains data from a simple (i.e. non-cluster) two-phase forest inventory conducted in 2007 that was used in \citet{mandallaz2013b} as a case study. The $s_1$ sample is comprised of 306 sample locations arranged on a systematic grid containing auxiliary information in the form of LiDAR canopy height metrics (\code{mean}, \code{stddev}, \code{max}, \code{q75}). For a systematic subsample of 67 ($s_2$ sample), terrestrial information of the timber volume per hectare (\code{tvol}) on the sample plot level is provided from a terrestrial survey. We can load \pkg{forestinventory} and examine the \code{grisons} data set in the \proglang{R} environment as follows:

@@

The \textbf{exhaustive estimator} can be applied by additionally passing a vector containing the \textit{exact} means of the explanatory variables, i.e. $\bar{\pmb{Z}}$, to the optional argument \code{exhaustive}. This vector must be calculated beforehand in such a way that any desired boundary adjustment has already been applied. Note that the vector input to \code{exhaustive} must be in the same order that the \code{lm()}-function processes a \code{formula} object including the intercept term whose exact mean will always be 1. Particular caution must be taken if categorical variables are present because the \code{lm()}-function, which is internally used to set up the design-matrix, automatically creates dummy variables with one of the categories used as a reference. Using our \code{grisons} example, the correct order can always be extracted by the following \proglang{R}-code:

@@

In the equations for the point estimates (Eq. \ref{eq:pointest_2p_small} and \ref{eq:pepsmall}), we see that the globally derived regression coefficients are applied to the exhaustively or non-exhaustively calculated means of the explanatory variables ($\bar{\pmb{Z}}_G$, $\hat{\bar{\pmb{Z}}}_G$) which are now only based on the first-phase sample $s_{1,G}$ located within small area $G$. A potential bias of the regression model predictions in the small area $G$, due to fitting the regression model with data also outside of $G$, is then corrected by adding the mean of the empirical model residuals in $G$. This is called the \textit{bias} or \textit{residual correction} term.

@@

where the variance-covariance matrix of the auxiliary vector $\hat{\bar{\pmb{Z}}}_G$ is estimated by
\begin{equation}\label{estvarcovaux_G}
\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{G}}=
\frac{1}{n_{1,G}(n_{1,G}-1)}\sum_{x\in{s_{1,G}}}
(\pmb{Z}(x)-\hat{\bar{\pmb{Z}}}_{G})(\pmb{Z}(x)-\hat{\bar{\pmb{Z}}}_{G})^t
\end{equation}

@@

\begin{subequations}\label{eq:pest_2p_extsynth_extpsynth}
\begin{align}
\hat{Y}_{G,extsynth,2p} & = \bar{\pmb{\mathbb{Z}}}^t_{G}\hat{\pmb{\theta}}_{s_2} \label{eq:pointest_2p_extsynth} \\
\hat{Y}_{G,extpsynth,2p} & =\hat{\bar{\pmb{\mathbb{Z}}}}_{G}^t\hat{\pmb{\theta}}_{s_2} \label{eq:pointest_2p_extsynth} \\
\hat{\var}(\hat{Y}_{G,extsynth,2p}) & = \bar{\pmb{\mathbb{Z}}}^t_{G}\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{s_2}}\bar{\pmb{\mathbb{Z}}}_{G} \label{eq:var_2p_extsynth} \\
\hat{\var}(\hat{Y}_{G,extpsynth,2p})& =
\hat{\bar{\pmb{\mathbb{Z}}}}_{G}^t\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{s_2}}
\hat{\bar{\pmb{\mathbb{Z}}}}_{G}
+ \hat{\pmb{\theta}}^t_{s_2}\hat{\Sigma}_{\hat{\bar{\pmb{\mathbb{Z}}}}_{G}}\hat{\pmb{\theta}}_{s_2} \label{eq:var_2p_extpsynth}
\end{align}
\end{subequations}

@@

\begin{subequations}\label{eq:ext_varexternal_2p_extsynth}
\begin{align}
  \hat{\var}_{ext}(\hat{Y}_{G,extsynth,2p}) & = \frac{1}{n_{2,G}}\hat{\var}_{s_{2,G}}(\hat{\mathbb{R}}(x)) \label{eq:ext_varexternal_2p_extsynth} \\
  \hat{\var}_{ext}(\hat{Y}_{G,extpsynth,2p}) & = \frac{1}{n_{1,G}}\hat{\var}_{s_{2,G}}(Y(x)) + \Big(1-\frac{n_{2,G}}{n_{1,G}}\Big)\frac{1}{n_{2,G}}\hat{\var}_{s_{2_G}}(\hat{\mathbb{R}}(x)) \label{eq:ext_varexternal_2p_extpsynth}
\end{align}
\end{subequations}
where $\hat{\mathbb{R}}(x)$ are the empirical residuals under the extended auxiliary vector.

To summarize, the (pseudo) synthetic estimator can be applied whether terrestrial inventory sample is found in the small area or not, but has a deceptively small g-weight variance due to its potential bias.  When terrestrial sample is observed in the small area, we can produce (asymptotically) design-unbiased estimates and variances using either \textit{small} or \textit{psmall} which remove this bias directly with a mean residual term, or more elegantly with \textit{extsynth} or \textit{extpsynth} which simply use the same synthetic formulas while including an indicator variable for the small area in the model formula to remove the bias by construction in OLS.

@@

The \pkg{forestinventory} package automatically includes the indicator variable for the small area behind the scenes so there is no need for the user to implement it. Notice that the $R^2$s (\code{r.squared}) under the \textit{extpsynth} estimator vary between the small areas, while they are identical under the \textit{psmall} estimator. This is because under the \textit{extpsynth} estimator, the regression model is recalculated for each small area estimation after adding the indicator variable for the respective small area in the globally derived design matrix. In case of the  \textit{psmall} estimator, the regression model stays the same for each small area estimation. Although the results of both estimators should always be close to each other, we recommend applying both estimators and compare the results afterwards in order to reveal unsuspected patterns in the data, particularly in the case of cluster sampling (see Section \ref{sec:speccas_and_scen}).\par

@@

The \textbf{exhaustive versions} of the small area estimators (Eq. \ref{eq:pointest_2p_small}, \ref{eq:var_2p_reg_small}, \ref{eq:varext_2p_reg_small}, \ref{eq:pointest_2p_reg_synth}, \ref{eq:var_2p_reg_synth}) are specified via the optional argument \code{exhaustive}. Its application requires that we know the exact means of all explanatory variables within the small area(s) of interest. In contrast to the \textit{global} estimators, the exact means have now to be delivered in the form of a \code{data.frame}, where each row corresponds to a small area, and each column specifies the exact mean of the respective explanatory variable. Note that likewise the case of global estimation, the order of the explanatory variables in the data frame has to match the order in which they appear in the design matrix defined by the \code{lm()}-function in \proglang{R}. In order to tell \proglang{R} which row describes which small area, the row names have to match the respective names of the small areas specified in the \code{areas} argument.
